Human Activity Recognition Assigenment
========================================================

## Data Loading


```{r fig.width=7, fig.height=6}
testData <- read.csv(file="pml-testing.csv", header = TRUE, na.strings = c("", "NA"))
trainData <- read.csv(file="pml-training.csv", header = TRUE, na.strings = c("", "NA"))
```

Now wen need to remove the first column which contain Ids

```{r}
testData <- testData[,-1]
trainData <- trainData[,-1]
```

The Data Set is `r dim(trainData)[1]` by `r dim(trainData)[2]`

Because of Using Instances based learning (i.e K Nearest Nighbor) KNN algorithm to predict, and the data set is large, it is better to remove columns and rows with huge number of missing values.
Any column contains missing values had been excluded, this is not the best thing to handle missing values because we could lost valuble variable with just one or two missing values. But it showed outstanding results.

```{r}
x=0
for(i in 1:length(names(trainData)))
{
  if(sum(is.na(trainData[,i])) > 0)
    x <- c(x,i)
    
}
HAR <- trainData[,-x[2:length(x)]]
```

Now our Data Set is `r dim(HAR)[1]` by `r dim(HAR)[2]` 


## Sampling

Partitoning data into training and testing sets, 70% for Training and 30% for Testing
```{r }
library(caret)
inTrain <- createDataPartition(HAR$classe, p = .7)[[1]]
training <- HAR[inTrain,]
testing <- HAR[-inTrain,]
```

We can compare the distribution of prediction class
```{r}
prop.table(table(training$classe)) * 100
prop.table(table(testing$classe)) * 100
```


## Training

KNN had been used for with centering and scalling preprocessing

```{r cache=TRUE}
library(caret)
set.seed(400)
knnFit <- train(classe ~ ., data = training, method = "knn", preProcess = c("center","scale"))
```

Output of kNN model
```{r}
knnFit
```

Plotting yields Number of Neighbours Vs accuracy
```{r}
plot(knnFit)
```


## Test Prediction 

Here we predict on the testing set, and show the confusion matrix 

```{r}
knnPredict <- predict(knnFit,newdata = testing )
confusionMatrix(knnPredict, testing$classe )
```

The Out of sample error rate is `r 1-mean(knnPredict == testing$classe)`


## Submision Predictions

Now We can apply the model to predict the unknown values, and seave them into text files.
```{r}
FinalPredict <- predict(knnFit,newdata = testData )

write_files = function(x)
{
  n = length(x)
  for(i in 1:n)
  {
    filename = paste0("problem_",i,".txt")
    write.table(x[i],file=filename,quote=FALSE,row.names=FALSE,col.names=FALSE)
  }
}
write_files(FinalPredict)
FinalPredict
```

